The Right Way to Search Evolving Graphs

### 2016-02-20 paper.tex
clarify algorithm 1

The restriction that temporal paths may only traverse active nodes reflects
underlying structure in many real world applications, such as analyzing the
influence of nodes over social networks. We will also show later in
Section~\ref{sec:temp-paths-adjac}
that the resulting structure of allowable temporal paths leads to nontrivial
subtleties in the generalization of algorithms and concepts from ordinary
(static) graphs.

@@

The BFS on evolving graphs is described in Algorithm~\ref{alg:bfs}.
Given an evolving graph $G_n$ and a root $(v_1, t_1)$,
Algorithm~\ref{alg:bfs} returns all temporal notes reachable from the root and
their distances from the root.
$reached$ is a dictionary from temporal nodes to integers whose key set represents
all visited temporal nodes and whose value set are the corresponding distances
from the root.

>>>>

The restriction that temporal paths may only traverse active nodes reflects
underlying causal structure in many real world applications, such as analyzing the
influence of nodes over social networks. We will also show later in
Section~\ref{sec:temp-paths-adjac}
that the resulting structure of allowable temporal paths leads to nontrivial
subtleties in the generalization of algorithms and concepts from ordinary
(static) graphs.

@@

\subsection{Description of the Algorithm}
\label{sec:descr-algor}

The BFS on evolving graphs is described in Algorithm~\ref{alg:bfs}.
Algorithm~\ref{alg:bfs} is identical to the BFS on static graphs expect 
line $8$, where we visit the forward neighbors of a given temporal node
in both space and time.
Given an evolving graph $G_n$ and a root $(v_1, t_1)$,
Algorithm~\ref{alg:bfs} returns all temporal notes reachable from the root and
their distances from the root.
$reached$ is a dictionary from temporal nodes to integers whose key set represents
all visited temporal nodes and whose value set are the corresponding distances
from the root.
